Supporting information

### 2016-07-13 gm_pce/manuscript_gmes.Rmd
final edits, submitted to PCE

**Table 1**. Leaf morphological and physiological traits of sun and shade leaves under ambient and elevated temperature treatments for *Eucalyptus tereticornis*. Leaf mass per area (LMA, g m^2^), leaf nitrogen per unit area (*N*~a~, gN m^-2^), $\delta$^13^C (&permil;), pre-dawn leaf water potential ($\Psi$~pd~, MPa), midday leaf water potential ($\Psi$~L~, MPa) and leaf-specific hydraulic condctance (*K*~L~, mmol m^-2^ s^-1^ MPa^-1^) are given as treatment means (&pm; 1 standard error) across six measurement campaigns. Values of *V*~cmax~ and *J*~max~ are treatment mean (&pm; 1 standard error) from A-*C*~i~ curves measured in each chamber at 25 &deg;C and saturating light. Different letters represent significant differences between leaf type and temperature treatments (based on a Tukey test). The P value represents the overall effect between each unique combination of leaf type and temperature treatment for each trait.

>>>>

**Table 1**. Leaf morphological and physiological traits of sun and shade leaves under ambient and elevated temperature treatments for *Eucalyptus tereticornis*. Leaf mass per area (LMA, g m^2^), leaf nitrogen per unit area (*N*~a~, gN m^-2^), $\delta$^13^C (&permil;), pre-dawn leaf water potential ($\Psi$~pd~, MPa), midday leaf water potential ($\Psi$~L~, MPa) and leaf-specific hydraulic conductance (*K*~L~, mmol m^-2^ s^-1^ MPa^-1^) are given as treatment means (&pm; 1 standard error) across six measurement campaigns. Values of *V*~cmax~ and *J*~max~ are treatment mean (&pm; 1 standard error) from A-*C*~i~ curves measured in each chamber at 25 &deg;C and saturating light. Different letters represent significant differences between leaf type and temperature treatments (based on a Tukey test). The P value represents the overall effect between each unique combination of leaf type and temperature treatment for each trait.

### 2016-07-13 gm_pce/manuscript_gmes_SuppInfo.Rmd
final edits, submitted to PCE

---
title: Supporting information
author: ""
date: ""
output:
  word_document:
    reference_docx: manuscriptstyle.docx
csl: new-phytologist.csl
bibliography: references.bib
---

@@

```{r echo=FALSE, warning=FALSE, message=FALSE, results='hide'}
source("gm_newphyt/manuscript_preload.R")
```

>>>>

---
title: Supporting information
author: ""
date: ""
output:
  word_document:
    reference_docx: manuscriptstyle_pce.docx
csl: plant-cell-environment.csl
bibliography: references.bib
---

@@

```{r echo=FALSE, warning=FALSE, message=FALSE, results='hide'}
source("gm_pce/manuscript_preload.R")
```
